---
title: "FUNding"
author: "Muricio Roca, Axel Cedholm, XXXXXXX Mikael Brink"
format: revealjs
editor: visual
---

## Background

The Swecris database enables you to search, compare and produce statistics for Swedish research projects.

-   Information from several research funding bodies is gathered in one place.

-   

    <https://www.vr.se/english/swecris.html#/>

## Retrieval of data

We used the swecris library available at github, <https://github.com/KTH-Library/swecris>.

```{r}
#| label: load-packages
#| echo: true
#| eval: false
 
#install
install_github("KTH-Library/swecris", dependencies = T, force=T)
#
library(swecris)
allfunding<-swecris::swecris_fundings()

#I modified the following function from swecris, and removed the search string that specified KTH
#kth_projects <- swecris_funding()

swecris_all_university_projects <- function (searchstring = "", 
                                             token) 
{
  if (missing(token)) 
    token <- "RWNDZ3FDRVVSMmNUNlZkMkN3"
  httr::GET("https://swecris-api.vr.se/v1/scp/export", query = list(`organizationType[]` = "Universitet", 
                                                                    sortOrder = "desc", sortColumn = "FundingStartDate", 
                                                                    searchText = URLencode(searchstring), token = token)) %>% 
    httr::content(as = "text", encoding = "UTF-8") %>% readr::read_delim(delim = ";", 
                                                                         quote = "\"", show_col_types = FALSE)
}
```

##  Background cont.

The

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```
