---
title: "FUNding"
author: "Muricio Roca, Axel Cedholm, Joel Hallgren, Jose A. L. V., Evelyn Halitzki, Mikael Brink"
format: revealjs
editor: visual
---

## Background

The Swecris database enables you to search, compare and produce statistics for Swedish research projects.

-   Information from several research funding bodies is gathered in one place.

    <https://www.vr.se/english/swecris.html#/>

## Retrieval of data

We used the swecris library available at github, <https://github.com/KTH-Library/swecris> to download the data.

```{r}
#| label: load-packages
#| echo: true
#| eval: false
 
#install
install_github("KTH-Library/swecris", dependencies = T, force=T)
#
library(swecris)
allfunding<-swecris::swecris_fundings()

#I modified the following function from swecris, and removed the search string that specified KTH
#kth_projects <- swecris_funding()

swecris_all_university_projects <- function (searchstring = "", 
                                             token) 
{
  if (missing(token)) 
    token <- "RWNDZ3FDRVVSMmNUNlZkMkN3"
  httr::GET("https://swecris-api.vr.se/v1/scp/export", query = list(`organizationType[]` = "Universitet", 
                                                                    sortOrder = "desc", sortColumn = "FundingStartDate", 
                                                                    searchText = URLencode(searchstring), token = token)) %>% 
    httr::content(as = "text", encoding = "UTF-8") %>% readr::read_delim(delim = ";", 
                                                                         quote = "\"", show_col_types = FALSE)
}
#get the data to an object
all_university_projects <- swecris_all_university_projects()

```

## Background cont.

```{r, echo=F}
library(tidyverse)
library(gt)
all_university_projects <- readRDS("all_university_projects.RDS")
```

The downloaded data contains these headers, and contains

-   There are **`r nrow(all_university_projects)`** projects in our data.
-   There are **`r all_university_projects %>% distinct(FundingOrganisationNameEn) %>% count()`** unique funding organizations
-   There are **`r all_university_projects %>% distinct(CoordinatingOrganisationNameEn) %>% count()`** unique coordinating organizations
-   The database also contained an abstract for each project.

```{r}

all_university_projects %>% colnames()
```

## Aim

-   Rshiny- app to display and interactively change

    -   **Descriptive data**

    -   A **map** displaying the geographical distribution of funds in Sweden for Universities.

    -   **Word cloud** displaying the most prevalent words for the respective research field

    -   Information related to the **Grant applicants**

## Challenges

-   Bla bla bla
